Fast and Error-Adaptive Count-Distinct Sketch \\for Influence Maximization

### 2021-01-12 paper.tex
progress

\subsection{Error-Adaptive Sketch Rebuilding}

@@

Two threshold values allow the algorithm to rebuild after large local errors but skip rebuilding if the error is minuscule relative to the total score. 
If a rebuild is not required, we only update the $mask$ by merging it with the candidate vertex's sketch. 
This approach allows us to keep sketches high quality even after many vertices are added to the seed set, but on the other hand, forces us to perform Monte-Carlo simulations which can be expensive. We reuse the reachability sets of latent seed set, $R_G(S')$, computed by Monte-Carlo simulations. While rebuilding sketches, $R_G(S')$ is used to check whether if a vertex is blocked in a sample.

@@

\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=\linewidth]{images/sketch-diffusion.pdf}
\caption{(a) The initial state on the toy graph for \acro{}; all vertices have set as live(green) and their registers initialized with leading zero count of their hashes. (b) 
% For all live edges,$e_{ij}$, respective registers are merged and set to source vertex $j$'s register, $M_j \leftarrow Max(M_i, M_j)$. 
For the live edge between Vertex 1 and 4, the register is set to the maximum of the respective register. Since the first register of vertex 1 is bigger, we only update the second register. Also, the edge between vertex 4 and 3 is only live in simulation 2, so we only set the maximum of those two registers to vertex 4's second register. Notice that, we are moving registers in reverse, from target to source of the edges. We set vertices 1 and 4 as live(green) since their registers have changed in this iteration (c) Vertex 1's register is updated and set as live again since vertex 4's registers are changed.  (d) All vertices have registers converged, there are no live vertices. }\label{fig:hf-processing} 
\end{center}
\end{figure*}

>>>>

\begin{figure*}[!ht]
    \begin{center}
    \includegraphics[width=\linewidth]{images/sketch-diffusion.pdf}
    \caption{(a) The initial state on the toy graph for \acro{}; all vertices have set as live(green) and their registers initialized with leading zero count of their hashes. (b) 
    % For all live edges,$e_{ij}$, respective registers are merged and set to source vertex $j$'s register, $M_j \leftarrow Max(M_i, M_j)$. 
    For the live edge between Vertex 1 and 4, the register is set to the maximum of the respective register. Since the first register of vertex 1 is bigger, we only update the second register. Also, the edge between vertex 4 and 3 is only live in simulation 2, so we only set the maximum of those two registers to vertex 4's second register. Notice that, we are moving registers in reverse, from target to source of the edges. We set vertices 1 and 4 as live(green) since their registers have changed in this iteration (c) Vertex 1's register is updated and set as live again since vertex 4's registers are changed.  (d) All vertices have registers converged, there are no live vertices. }\label{fig:hf-processing} 
    \end{center}
    \end{figure*}
\subsection{Error-Adaptive Sketch Rebuilding}

@@

The use of two threshold values allows the algorithm to rebuild after large local errors but skip rebuilding if the error is minuscule relative to the total score. 
If a rebuild is not required, we only update the $mask$ by merging it with the candidate vertex's sketch. 
This approach allows us to keep sketches high quality even after many vertices are added to the seed set, but on the other hand, forces us to perform Monte-Carlo simulations which can be expensive. We reuse the reachability sets of latent seed set, $R_G(S')$, computed by Monte-Carlo simulations. While rebuilding sketches, $R_G(S')$ is used to check whether if a vertex is blocked in a sample.

@@

\begin{figure*}[!h]
    \begin{center}
        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_time.pdf}
        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_time.pdf}
        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_time.pdf}\\

        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_score.pdf}
        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_score.pdf}
        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_score.pdf}\\
    \end{center}
    \caption{Effect of $\epsilon$ parameters on \acro's performance.}\label{fig:parameter-smallmultiples} 
\end{figure*}

Our method's performance, both in terms of speed and quality of results, depends on parameter selection. 
Even though,
